### 2025-05-07 project2/nnMetamodels.tex
final draft

At any time $t=1,\ldots,T$, the insurer's liability in a \gls{va} contract is the present value of all payments, net of the fee income.
For example, suppose that the per-period risk-free rate is $r$, then
\textcolor{red}{the insurer's time-$t$ liability for a \gls{gmwb} contract is}

@@

@@

Figure~\ref{fig2:tailMatches} depicts the average percentage of correctly identified true tail scenarios by different metamodels for increasing safety margins.
Each quantity is averaged over $100$ macro replications.
For a fixed safety margin, the percentage of tail matches of the traditional regression metamodels are substantially lower than the ones of the neural networks.
We observe that a poor metamodel such as the \gls{qpr} identifies less than $40\%$ of the true tail scenario without any safety margin.
In contrast, a well-suited metamodel such as the \gls{lstm} identifies more than $75\%$ of the true tail scenarios without any safety margin and more than the \gls{qpr} metamodel does with $15\%$ of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies $100\%$ of the true tail scenarios on with a $10\%$ safety margin for a \gls{gmab} contract.
The \gls{gmab} contract is simpler than the \gls{gmwb} contract, and the true tail scenarios are easier to identify. 
For a \gls{gmab}, our \gls{lstm} metamodel identifies $100\%$ of the true tail scenarios with a $2.5\%$ safety margin}.
The \gls{rnn} metamodel suffers from the vanishing gradient problem during the training stage. 
For some macro replications (as shown in Figure~\ref{subfig2:badRNN}), the \gls{rnn} metamodels' predictions are far from the true losses, especially on the tails.
Seperating the good training macro replications from the bad ones, the results reconcile with the findings in Table~\ref{tab:gmwb_arch}.
The \gls{fnn} metamodel has a better fit than the regression metamodels, but it does not have the same level of accuracy as the \gls{lstm} metamodel, which is a specialized network to capture the sequential structure of our time-series features.
For comparison, the horizontal dotted line shows the percentage of correctly identified true tails for the standard nested simulation procedure.
A good metamodel should be able to identify a similar percentage of true tail scenarios as the standard procedure does with a reasonable safety margin.
Otherwise, the two-stage procedure will offer no computational advantage in simulation budget over the standard procedure.
The \gls{lstm} metamodel can reach similar percentage \textcolor{red}{of correctly identified true tail scenarios} with a $5\%$ safety margin.
This indicates that the \gls{lstm} metamodel should be able to reach the same level of accuracy as the standard procedure with only $20\%$ of the simulation budget.

>>>>

At any time $t=1,\ldots,T$, the insurer's liability in a \gls{va} contract is the present value of all payments, net of the fee income.
For example, suppose that the per-period risk-free rate is $r$, then
the insurer's time-$t$ liability for a \gls{gmwb} contract is

@@

In the two-stage procedure, the neural network metamodel approximates $L$ in Equation~\ref{eq2:lossrv}, where 
\begin{equation}
    L = L(\mathbf{S}_T) = L(\Delta_0, \ldots, \Delta_{T-1}, S_0, \ldots, S_T)
\end{equation}
The loss $L$ depends on all the hedging weights $\Delta_0, \ldots, \Delta_{T-1}$, which are determined by the stock prices $S_t$, $t=0,\ldots,T-1$.
In addition, $L$ also depends on all the stock prices $S_0, \ldots, S_T$ directly.
Therefore, the loss $L(\mathbf{S}_T)$ is a complex function of the entire stock price path $\mathbf{S}_T$, and the neural network metamodel $\Lhat^{PD}(\mathbf{X})$ approximates $L(\mathbf{S}_T)$ by mapping the stock returns $\mathbf{X}_T$ to the loss $L(\mathbf{S}_T)$.
Statistically speaking, $L(\mathbf{S}_T)$ is a random variable whose stochasticity solely depends on the stock price path $\mathbf{S}_T$. 
Nevertheless, $L(\mathbf{S}_T)$ can be viewed as a function of the underlying stock returns $\mathbf{X}_T$ and can be approximated by a neural network metamodel.

@@

Figure~\ref{fig2:tailMatches} depicts the average percentage of correctly identified true tail scenarios by different metamodels for increasing safety margins.
Each quantity is averaged over $100$ macro replications.
For a fixed safety margin, the percentage of tail matches of the traditional regression metamodels are substantially lower than the ones of the neural networks.
We observe that a poor metamodel such as the \gls{qpr} identifies less than $40\%$ of the true tail scenario without any safety margin.
In contrast, a well-suited metamodel such as the \gls{lstm} identifies more than $75\%$ of the true tail scenarios without any safety margin and more than the \gls{qpr} metamodel does with $15\%$ of safety margin\footnote{The metamodel in~\cite{dang2020efficient} identifies $100\%$ of the true tail scenarios on with a $10\%$ safety margin for a \gls{gmab} contract.
The \gls{gmab} contract is simpler than the \gls{gmwb} contract, and the true tail scenarios are easier to identify. 
For a \gls{gmab}, our \gls{lstm} metamodel identifies $100\%$ of the true tail scenarios with a $2.5\%$ safety margin}.
The \gls{rnn} metamodel suffers from the vanishing gradient problem during the training stage. 
For some macro replications (as shown in Figure~\ref{subfig2:badRNN}), the \gls{rnn} metamodels' predictions are far from the true losses, especially on the tails.
Seperating the good training macro replications from the bad ones, the results reconcile with the findings in Table~\ref{tab:gmwb_arch}.
The \gls{fnn} metamodel has a better fit than the regression metamodels, but it does not have the same level of accuracy as the \gls{lstm} metamodel, which is a specialized network to capture the sequential structure of our time-series features.
For comparison, the horizontal dotted line shows the percentage of correctly identified true tails for the standard nested simulation procedure.
A good metamodel should be able to identify a similar percentage of true tail scenarios as the standard procedure does with a reasonable safety margin.
Otherwise, the two-stage procedure will offer no computational advantage in simulation budget over the standard procedure.
The \gls{lstm} metamodel can reach similar percentage of correctly identified true tail scenarios with a $5\%$ safety margin.
This indicates that the \gls{lstm} metamodel should be able to reach the same level of accuracy as the standard procedure with only $20\%$ of the simulation budget.

### 2025-05-07 project3/draft.tex
asd
final draft

\subsection{Rapid Adaptation of \gls{lstm} Metamodels} \label{sec3:transfer_learning}

@@

In this section, we evaluate the performance of the \gls{tl} framework for rapid adaptation of \gls{lstm} metamodels in dynamic hedging of \gls{va}s.
The low noise dataset generated by the standard nested simulation procedure in Section~\ref{sec2:numerical} is used to train the source \gls{lstm} metamodels.
We consider \gls{tl} to two types of target tasks: 
\begin{itemize}
    \item the same contract but different underlying asset model, and
    \item different contracts but the same asset model.
\end{itemize}  
Similar to Section~\ref{sec2:numerical}, we use the standard nested simulation procedure to generate the dataset for the source and target tasks.
Serveral \gls{va} datasets generated with the standard nested simulation procedures under geometric Brownian motion (\gls{gbm}) and regime-switching \gls{gbm} (\gls{rsgbm}) asset models.
\textcolor{red}{In this experiment, we use the same \gls{rsgbm} asset model as Chapter~\ref{chap:project2} to generate the dataset for the source and target tasks.}
\textcolor{red}{When following a static lapse model and a dynamic lapse model, the monthly lapse rate is given by Equation~\ref{eq:lapse_rate} and Equation~\ref{eq:dynamic_lapse_rate}, respectively.}
\textcolor{red}{The experiments are run on a machine with a AMD Ryzen 9 7900X processor with 32 GB of RAM and a Nvidia RTX $\num{3060}$ Ti GPU}

>>>>

\subsection{Rapid Adaptation of LSTM Metamodels} \label{sec3:transfer_learning}

@@

In this section, we evaluate the performance of the \gls{tl} framework for rapid adaptation of \gls{lstm} metamodels in dynamic hedging of \gls{va}s.
The low noise dataset generated by the standard nested simulation procedure in Section~\ref{sec2:numerical} is used to train the source \gls{lstm} metamodels.
We consider \gls{tl} to two types of target tasks: 
\begin{itemize}
    \item the same contract but different underlying asset model, and
    \item different contracts but the same asset model.
\end{itemize}  
Similar to Section~\ref{sec2:numerical}, we use the standard nested simulation procedure to generate the dataset for the source and target tasks.
Serveral \gls{va} datasets generated with the standard nested simulation procedures under geometric Brownian motion (\gls{gbm}) and regime-switching \gls{gbm} (\gls{rsgbm}) asset models.
In this experiment, we use the same \gls{rsgbm} asset model as Chapter~\ref{chap:project2} to generate the dataset for the source and target tasks.
When following a static lapse model and a dynamic lapse model, the monthly lapse rate is given by Equation~\ref{eq:lapse_rate} and Equation~\ref{eq:dynamic_lapse_rate}, respectively.
The experiments are run on a machine with a AMD Ryzen 9 7900X processor with 32 GB of RAM and a Nvidia RTX $\num{3060}$ Ti GPU.
